Big Brother Is Watching

### 2015-11-05 manuscript.tex
changes'

\section{Abstract}
\label{sec:abstract}
Several models were developed to facilitate the perpetual surveillance of Gotham City using Micro unmanned Aerial Vehicles in order to catch jaywalkers. These models are optimized to handle separate scenarios involving maximum visit intervals, sharp turns requiring more energy/fuel, recharging/fueling rates, densities of jaywalkers, and the biased knowledge of the drone programmers. We represent Gotham City as rectangular grid in order to simplify our models. Our three approaches that handle these problems consist of an optimal path/contingency model that minimizes the number of turns and accounts for drone failures, a blocking model that subdivides Gotham in to smaller rectangles that individual drones traverse, and a greedy random walk model that adds a randomized effect to the drones paths.
\section{General Assumptions}
\label{sec:general_assumptions}
\paragraph{Representing Manhattan}
\label{par:representing_manhattan}
First, we want to justify our representation of Manhattan. Manhattan is a long thin strip of land, spanned vertically by \emph{avenues} and horizontally by \emph{streets}. Manhattan is effectively 250 streets long, and 10 avenues wide. A Manhattan city block is \SI{80}\m by \SI{274}\m. We can approximate Manhattan, or at least this hypothetical version of Manhattan as part of Gotham City, to be a grid 250 blocks long by 30 blocks wide, where a block is an arbitrary unit of distance, in this case \SI{80}\m. In this representation, Central Park is 10 blocks wide and 51 blocks long, since the real Central Park is 3 avenues wide and goes from \nth{59} Street to \nth{110} Street, occupying the middle 3 avenues \cite{centralpark}. Similarly, if we take Gotham University to be the fictional equivalent of Columbia University, which is found between \nth{110} Street and \nth{122} Street and spans the 3 westernmost avenues of Manhattan \cite{columbia}, then we can it to be an area 12 block long and 9 blocks wide. Finally, the Financial District is contained in the southernmost 20 streets in Manhattan \cite{financial}, hence we can make it occupy the last 20 rows in our matrix.

@@

This method can be extended to the case where some areas must be observed more often than others. We can just assume that these areas are rectangular (which is a fairly good assumption in this case) and treat these areas as separate blocks.

@@

\subsection{Contingency Source}
\label{sub:contingency_source}
\lstinputlisting{models/drone_failures.m}

>>>>

\section{Abstract}
\label{sec:abstract}
Several models were developed to facilitate the perpetual surveillance of Gotham City using . These models account

\section{General Assumptions}
\label{sec:general_assumptions}
\paragraph{Representing Manhattan}
\label{par:representing_manhattan}
First, we want to justify our representation of Manhattan. Manhattan is a long thin strip of land, spanned vertically by \emph{avenues} and horizontally by \emph{streets}. Manhattan is effectively 250 streets long, and 10 avenues wide. A Manhattan city block is \SI{80}\m by \SI{274}\m. We can approximate Manhattan, or at least this hypothetical version of Manhattan as part of Gotham City, to be a grid 250 blocks long by 30 blocks wide, where a block is an arbitrary unit of distance, in this case \SI{80}\m. In this representation, Central Park is 10 blocks wide and 51 blocks long, since the real Central Park is 3 avenues wide and goes from \nth{59} Street to \nth{110} Street, occupying the middle 3 avenues \cite{centralpark}. Similarly, if we take Gotham University to be the fictional equivalent of Columbia University, which is found between \nth{110} Street and \nth{122} Street and spans the 3 westernmost avenues of Manhattan \cite{columbia}, then we can it to be an area 12 block long and 9 blocks wide. Finally, the Financial District is contained in the southernmost 20 streets in Manhattan \cite{financial}, hence we can make it occupy the last 20 rows in our matrix.

@@

The blocking method can be extended to the case where some areas must be observed more often than others. We can just assume that these areas are rectangular (which is a fairly good assumption in this case) and treat these areas as separate blocks. We can use the previous algorithm to calculate how many drones the high- or low-surveillance blocks need. The areas of Manhattan without special surveillance requirements now form a rectangular region with rectangular "holes" in it. Therefore, we split this complicated region into a collection of rectangles that are as large as possible (see figure \ref{blocking2}, and then run the algorithm on each of these rectangles. There are multiple ways to do this, so we test each configuration to find which one requires the fewest total drones. Finally, we add the number of drones required to cover each rectangle to find the total number of drones required to survey Manhattan. Finally, we take the minimum of this number and the number of drones it would take if we just visited all regions as often as the most covered region needs.

\begin{figure}[htb!]
    \centering{{\includegraphics[width=8cm]{figures/blocking.pdf} }}
    \caption{Different ways to divide Manhattan into rectangular blocks; in this simplified diagram, the middle (red) region is Central Park, and the other (yellow) regions are the rest of Manhattan.}
    \label{blocking2}
\end{figure}

In this model (Central Park is visited every 20 minutes, and the financial district and Gotham University [which we modeled as Columbia University] every 5, we got 63 for the number of drones.

@@
